\documentclass[letterpaper,12pt]{article}
\usepackage{tabularx} % extra features for tabular environment
\usepackage{amsmath}  % improve math presentation
\usepackage{graphicx} % takes care of graphic including machinery
\usepackage[margin=1in,letterpaper]{geometry} % decreases margins
\usepackage{cite} % takes care of citations
\usepackage[final]{hyperref} % adds hyper links inside the generated pdf file
\hypersetup{
	colorlinks=true,       % false: boxed links; true: colored links
	linkcolor=blue,        % color of internal links
	citecolor=blue,        % color of links to bibliography
	filecolor=magenta,     % color of file links
	urlcolor=blue         
}
\usepackage{blindtext}
\usepackage{dirtree}
\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

	\lstset{frame=tb,
	language=Java,
	aboveskip=3mm,
	belowskip=3mm,
	showstringspaces=false,
	columns=flexible,
	basicstyle={\small\ttfamily},
	numbers=none,
	numberstyle=\tiny\color{gray},
	keywordstyle=\color{blue},
	commentstyle=\color{dkgreen},
	stringstyle=\color{mauve},
	breaklines=true,
	breakatwhitespace=true,
	tabsize=3
}

%++++++++++++++++++++++++++++++++++++++++


\begin{document}
	
	\title{File Calc}
	\author{Cyber Solutions Development - Georgia}
	\date{\today}
	\maketitle
	
	\begin{abstract}
		Your task is to build file parser that conforms to the attached format and solve the equations, given two directories that contain 'M' files and with each file containing 'N' equations.
	\end{abstract}
	
	
	\section{Requirements}
	
	In this assignment, you will build an application that will compute equations that are read in from a binary file.
	
	\subsection{Basic Requirements}
		\begin{enumerate}
			\item Written in C
			\item Take two arguments that are directories: Input and Output directory. Report error if not directory.
			\item Successfully parses the binary file. Report error otherwise.
			\item Handle bad inputs such as bad format as described above, divide by zero, or interger overflow. Report error otherwise.
			\item Single binary with the usage statement ./simplecalc input\_dir output\_dir	
			\item All files should have the following memory permissions: -,rw-, r-\--, r-\--. Report error otherwise.
			\item Use the read, write, lseek, open, close, and creat system calls. See man pages for usages. 
			\item Read environment variables to determine logging level.
	\end{enumerate}
	
	\subsection{Specific Requirements}
	\subsubsection{Required Operators}
		\begin{enumerate}
			\item Addition 
			\item Subtraction
			\item Multiplication
			\item Division
			\item Modulo 
			\item Left shift 
			\item Right shift 
			\item And
			\item Or
			\item XOR
			\item Rotate Left
			\item Rotate Right
		\end{enumerate}
	
	\subsubsection{Data Structures}
	Use an array to hold the data for each file. Use dynamic memory allocation on the heap to hold all file data.
	
	\subsubsection{Memory Management}
	Your program should not be leaking memory. Your program should show no memory leaks with:
		\begin{lstlisting}
			valgrind --leak-check=full ./filecalc input_dir output_dir 
		\end{lstlisting}
	
	\subsubsection{Assumptions}
		\begin{enumerate}
			\item All numbers are little endian
			\item All numbers are 64-bits in size
			\item All numbers should be treated as signed (int64\_t)
		\end{enumerate}
	\subsubsection{FileFormat}
		\begin{enumerate}
			\item Please see the attached FileSpec.pdf file.
		\end{enumerate}
	\subsubsection{Logging}
		\begin{enumerate}
			\item Your program must write all status, errors, and debug output to a seperate file called:
			\begin{lstlisting}
						top_level_dir/logs/(TimeStamp)-FileCalc.log
			\end{lstlisting}
			\item Your program will read from the FILECALC\_LOG\_LEVEL environment variable which will be a one-byte value:
			\begin{enumerate}
				\item 0: DEBUG - Used for development only
				\item 1: INFO - Default value if environment variable is not set or does not exist
				\item 2: WARNING - File Format errors
				\item 3: ERROR - Directories don't exist
			\end{enumerate}
			\item Your program will only log events that are greater than or equal to the value of the environment variable.
			\item Formatting is your choice.
			\item (ADVANCED) Implement a binary log format, please document it for your mentor and include a python3 parser. Note this is an excellent way to complete more JQR items that are in the python3 portion.

		\end{enumerate}
	\subsubsection{Special Requirements}
		\begin{enumerate}
			\item If your program receives an incorrectly formatted file: Log a warning and move that file to a seperate directory called BadFiles.
			\item Utilize the C preprocessor (or some other means) to write debug output when specified.
		\end{enumerate}
	\section{Deliverables}
	Your code should have the following file structure:
	\dirtree{%
	.1 FileCalc.
	.2 src.
	.3 source-files.
	.2 hdrs.
	.3 file-calc.h.
	.2 docs.
	.3 documentation.
	.2 CMakeLists.txt.
	}\hfill

	Your code should build and compile with the following shell script ran from the FileCalc directory:

	\begin{lstlisting}
	// build.sh
	mkdir build
	cd build
	cmake .. 
	make
	\end{lstlisting}
	
	
	\section{Notes to grader}
	The purpose of this assignment is to start writing complex C code. Use this assignment to achieve the following objectives:
	\begin{enumerate}
		\item Perform file input and output operations using system calls
		\item Building on CMake knowledge. Have your mentee experiment with using debug macros and building debug/release builds
		\item Code organization. This is complex project, and code organization will be key. Ensure your mentee is leverging good practices for code organization.
		\item Memory Management: Your mentee should be utilizing the heap for this project. Make sure your mentee understands valgrind and its purpose, and the important of clean memory management. 
	\end{enumerate}

	\section{JQR Sections Potentially Covered - Mentor Dependent}
	\begin{itemize}
		\item 4.1.5 (all)
		\item 4.1.7 (all)
		\item 4.1.8 (all)
		\item 4.1.9 (all)
		\item 4.1.10
		\item 4.1.11 (all)
		\item 4.1.12 (all)
		\item 4.1.18 (all)
		\item 4.1.19
		\item 4.1.20 (all)
		\item 4.1.21
		\item 4.1.22
		\item 4.1.23
	\end{itemize}
	
	
\end{document}
